---
title: "Versions of Cohen's $d$"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    toc: yes
    toc_float: yes
---

```{r include=FALSE}

knitr::opts_chunk$set(message = FALSE, 
                      warning = FALSE)

```

# Dependencies 

```{r}

library(tidyverse)
library(effsize)
library(metafor)
library(knitr)
library(kableExtra)
library(broom)
library(esci) # devtools::install_github("rcalinjageman/esci")

# multivariate meta analysis function
fit_mv_meta <- function(data){
  rma.mv(yi     = es,
         V      = variance, 
         random = ~ 1 | condition,
         slab   = paste0(condition, ": ", dv),
         data   = data)
}

cohens_ds <- function(data){
  # NB this requires that pre be the second level of the timepoint factor - ensure this is changed in wrangling
  require(effsize)
  fit <- effsize::cohen.d(score ~ timepoint,
                          paired = FALSE,
                          pooled = TRUE,
                          data = data)
  
  results <- 
    tibble(es       = fit$estimate,
           ci_lower = fit$conf.int[1],
           ci_upper = fit$conf.int[2]) %>%
    mutate(variance = ((ci_upper - ci_lower) / (1.96*2))^2)
  
  return(results)
}

glass_delta <- function(data){
  # NB this requires that pre be the second level of the timepoint factor - ensure this is changed in wrangling
  require(effsize)
  fit <- effsize::cohen.d(score ~ timepoint,
                          paired = FALSE,
                          pooled = FALSE,
                          data = data)
  
  results <- 
    tibble(es       = fit$estimate,
           ci_lower = fit$conf.int[1],
           ci_upper = fit$conf.int[2]) %>%
    mutate(variance = ((ci_upper - ci_lower) / (1.96*2))^2)
  
  return(results)
}

cohens_drm <- function(data){
  # NB this requires that pre be the second level of the timepoint factor - ensure this is changed in wrangling
  require(effsize)
  fit <- effsize::cohen.d(score ~ timepoint | Subject(id),
                          paired = TRUE,
                          pooled = TRUE,
                          data = data)

  results <- 
    tibble(es       = fit$estimate,
           ci_lower = fit$conf.int[1],
           ci_upper = fit$conf.int[2]) %>%
    mutate(variance = ((ci_upper - ci_lower) / (1.96*2))^2)
  
  return(results)
}

cohens_dav <- function(data){
  require(esci)
  
  # old: using summary stats
  # fit <- 
  #   esci::estimate_mdiff_paired(comparison_mean = data$mean_t2,
  #                               comparison_sd = data$sd_t2,
  #                               reference_mean = data$mean_t1,
  #                               reference_sd = data$sd_t1,
  #                               n = data$n,
  #                               correlation = data$r,
  #                               comparison_measure_name = "Comparison measure",
  #                               reference_measure_name = "Reference measure")
  
  fit <- data |>
    pivot_wider(id_cols = c(id, dv),
                names_from = timepoint, 
                values_from = score) %>%
    esci::estimate_mdiff_paired(data = .,
                                comparison_measure = post,
                                reference_measure = pre,
                                comparison_measure_name = "Comparison measure",
                                reference_measure_name = "Reference measure")

  return(tibble(es = fit$es_smd$effect_size,
                ci_lower = fit$es_smd$LL,
                ci_upper = fit$es_smd$UL,
                r  = fit$es_r$effect_size))
}

```

# Data wrangling

```{r}

# exclusions
data_processed <- read_csv("../../data/processed/data_processed_sabrinas_thesis.csv") %>%
  # recode conditions
  mutate(condition = paste(intervention, intervention_subtype),
         condition = str_remove(condition, " NA")) %>%
  select(id, 
         condition,
         dv1_pre_sum_score,
         dv2_pre_sum_score,
         dv3_pre_sum_score,
         dv1_post_sum_score,
         dv2_post_sum_score,
         dv3_post_sum_score,
         dv1_followup_sum_score,
         dv2_followup_sum_score,
         dv3_followup_sum_score) 

# reshaping
data_prepost <- data_processed %>%
  select(id,
         condition, 
         dv1_pre_sum_score,
         dv2_pre_sum_score,
         dv3_pre_sum_score,
         dv1_post_sum_score,
         dv2_post_sum_score,
         dv3_post_sum_score) %>%
  drop_na() %>%
  pivot_longer(names_to = "variable",
               values_to = "score",
               cols = c(dv1_pre_sum_score,
                        dv2_pre_sum_score,
                        dv3_pre_sum_score,
                        dv1_post_sum_score,
                        dv2_post_sum_score,
                        dv3_post_sum_score)) %>%
  mutate(variable = str_remove(variable, "_sum_score")) %>%
  separate(variable, into = c("dv", "timepoint"), sep = "_") 

```

# Sample sizes

```{r}

data_processed %>%
  count() %>%
  arrange() %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

```

# Differences between pre and post

## Cohen's $d_{s}$

```{r}

results_cohens_ds <- data_prepost %>%
  group_by(condition, dv) %>%
  do(cohens_ds(.)) 

fit_cohens_ds <- fit_mv_meta(results_cohens_ds)

forest(fit_cohens_ds, xlab = "Cohen's ds")

```

## Glass' $\Delta$

SDs are larger at post, providing a motivation for Delta over d.

```{r}

data_prepost %>%
  group_by(dv, timepoint) %>%
  summarize(sd = sd(score))

```

```{r}

results_glass_delta <- data_prepost %>%
  group_by(condition, dv) %>%
  do(glass_delta(.)) 

fit_glass_delta <- fit_mv_meta(results_glass_delta)

forest(fit_glass_delta, xlab = "Glass' Delta")

```

## Cohen's $d_{z}$

```{r}

results_cohens_dz <- data_prepost %>%
  pivot_wider(names_from = timepoint,
              values_from = score) %>%
  mutate(diff = post - pre) %>%
  group_by(condition, dv) %>%
  summarize(es = mean(diff)/sd(diff),
            n = n()) %>%
  group_by(condition, dv) %>%
  mutate(variance = (1/n)+(es^2/(2*n)), # variance calculated directly rather than estimating from CIs
         ci_lower = psych::cohen.d.ci(es, n1 = n)[1, "lower"],
         ci_upper = psych::cohen.d.ci(es, n1 = n)[1, "upper"])

fit_cohens_dz <- fit_mv_meta(results_cohens_dz)

forest(fit_cohens_dz, xlab = "Cohen's dz")

```

## Cohen's $d_{rm}$

NB I don't fully understand the internal method. I think it is Cohen's d_rm but am unclear from code and documentation.

```{r}

results_cohens_drm <- data_prepost %>%
  group_by(condition, dv) %>%
  do(cohens_drm(.))

fit_cohens_drm <- fit_mv_meta(results_cohens_drm)

forest(fit_cohens_drm, xlab = "Within-subjects Cohen's drm")

```

## Cohen's $d_{av}$

This is the only one that is all of (1) known internal workings, (2) good estimation width becuase it takes within subject non-independence into account, and (3) has congruent magnitude interpretations with Cohen's ds / can be meta analyzed with it / can't be accused of effect size inflation. 

Lakens 2013, Cummings 2016, esci package.

```{r}

results_cohens_dav <- data_prepost %>%
  group_by(dv, condition) %>%
  do(cohens_dav(.)) %>%
  mutate(variance = ((ci_upper - ci_lower) / (1.96*2))^2) %>%
  arrange(condition, dv)
  
fit_cohens_dav <- fit_mv_meta(results_cohens_dav)

forest(fit_cohens_dav, xlab = "Cohen's dav")

```

## Comparisons

```{r}

# combined effect sizes
results_effect_sizes <- 
  bind_rows(mutate(results_cohens_ds,   Method = "Cohen's ds"),
            mutate(results_glass_delta, Method = "Glass' Δ"),
            mutate(results_cohens_dz,   Method = "Cohen's dz"),
            mutate(results_cohens_drm,  Method = "Cohen's drm"),
            mutate(results_cohens_dav,  Method = "Cohen's dav")) %>%
  # combined meta effect sizes
  mutate(combined_conditions = paste(condition, dv, sep = ": "))

# meta effect sizes
results_meta_effect_sizes <- 
  tibble(Method = c("Cohen's ds",
                    "Glass' Δ",
                    "Cohen's dz",
                    "Cohen's drm",
                    "Cohen's dav"),
         es = c(fit_cohens_ds$b,
                fit_glass_delta$b,
                fit_cohens_dz$b,
                fit_cohens_drm$b,
                fit_cohens_dav$b),
         ci_lower = c(fit_cohens_ds$ci.lb,
                      fit_glass_delta$ci.lb,
                      fit_cohens_dz$ci.lb,
                      fit_cohens_drm$ci.lb,
                      fit_cohens_dav$ci.lb),
         ci_upper = c(fit_cohens_ds$ci.ub,
                      fit_glass_delta$ci.ub,
                      fit_cohens_dz$ci.ub,
                      fit_cohens_drm$ci.ub,
                      fit_cohens_dav$ci.ub)) %>%
  # combined meta effect sizes
  mutate(combined_conditions = "Meta")


bind_rows(results_effect_sizes, 
          results_meta_effect_sizes) %>%
  mutate(Method = fct_relevel(Method,
                              "Cohen's ds",
                              "Glass' Δ",
                              "Cohen's drm",
                              "Cohen's dav",
                              "Cohen's dz")) %>%
  ggplot(aes(combined_conditions, es, color = Method)) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = 0.5)) +
  geom_point(position = position_dodge(width = 0.5)) +
  coord_flip() +
  theme_linedraw() +
  xlab("") +
  ylab("Effect size") +
  guides(color = guide_legend(reverse = TRUE))
  
```

```{r}

ggplot(results_meta_effect_sizes, aes(Method, es)) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
  geom_point() +
  coord_flip() +
  theme_linedraw() +
  xlab("Method") +
  ylab("Meta effect size") 

```



